---
title: "TelecomAnalysis-Churn"
author: "Harmandeep Singh"
date: "14 November 2017"
output:
  pdf_document: default
  html_document: default
---
**Business Context**: Cell voice is one of the leading telecom providers. Customers of "Cell-Voice" are enrolled into one of 4 customer segments (customer categories) based on their billing and behavioural patterns.

1. Basic Service
2. E-Service
3. Plus Service
4. Total Service

The company is suffering from high attrition amongst its subscriber base. It wishes to launch an attrition management program which will target high risk customers. In order to understand the customers' behaviour and drivers of churn, the marketing team would like to perform the below analysis. 

The customer database contains demographic information (this information collected at the time of application) as well as Transactional details (i.e. usage, billing, enrolled plans etc). You can find the detailed variable description in next page. 

## Step-1 - Importing the Data
```{r setup, include=TRUE}

setwd("E:/R-Programing/TelecomAnalysis-Churn/")
cust_demo <- read.csv("cellvoice_demo.csv")
cust_trans <- read.csv("cellvoice_trans.csv")
```

## Step-2 - Understanding the data - Customer deomographics

```{r,echo=FALSE}
str(cust_demo)
summary(cust_demo)
head(cust_demo)
tail(cust_demo)
names(cust_demo)


```
## Step-2 Understanding the Data - Customer Transaction

```{r}
str(cust_trans)
summary(cust_trans)
names(cust_trans)
head(cust_trans)
tail(cust_trans)
```

## Step-3 Creating Customer 360
```{r}
require(dplyr)
cust_360 = cust_demo %>% left_join(cust_trans,by='CustID')

```
###**Analysis-1**
The marketing team would like to have high level summary of the data as follows. 
1. Identify which age group (from the below groups) have highest churn and what is percentage of churn.
  a. <=25
  b. 25-35
  c. 35-45
  d. 45-60
  e. >60
```{r}
cust_360<-cust_360 %>% mutate(age_seg = ifelse(age>60,"60+",ifelse(age>45 & age <60,"45-60",ifelse(age>35 & age<45,"35-45",ifelse(age>25 & age<35,"25-35","<25")))))

summary1 <- cust_360 %>% group_by(age_seg) %>% summarise(churn_cnt = sum(churn)) %>% ungroup() %>% mutate(churn_pct = churn_cnt/sum(churn_cnt))

data.frame(summary1)
```
*Based on the above analysis age group 25-35 has highest churn rate i.e 35%*

2. Summarize the data as follows at region and education level.
  a. Number of customers
  b. Number of churners
  c. Percentage of churners
  d. Average income
  e. Average Tenure
  f. Total revenue (Total revenue = longmon+tollmon+equipmon+cardmon+wiremon)
  
  
```{r}
summary2 <- cust_360 %>% group_by(region,ed) %>% summarise(TotalCust=n(),
                                                           TotalChurners=sum(churn),
                                                           PercentChurn=TotalChurners/TotalCust,
                                                           AverageIncome=mean(income,na.rm=T),
                                                           AverageTenure=mean(tenure,na.rm=T),
                                                           TotalRevenue=sum((longmon+tollmon + equipmon
                                                                                   +cardmon+wiremon), na.rm = T))
data.frame(summary2)
```
###**Analysis-2**
The marketing team would like to test/verify the following claims. 
1. Younger subscribers are more likely to churn as compared to older customers
2. Gender has no impact on Churn
3. Male subscribers are significantly older than females
4. Customer category has no impact on Churn
5. Customer categories show no gender bias
6. The longer a customer stays in the same address, less likely  to churn
7. Marital status affects the level of education of subscriber
8. Retired customers are more loyal
9. Test the impact of the following services on Churn
  o Toll free service
  o Equipment rental
  o Calling card service
  o Wireless service
10. Is there a regional impact on churn 

```{r}
### 1. Yes, Younger age group is more likely to churn
summarise(cust_360,avg = mean(churn,na.rm=T))

fit_age <- aov(churn ~ age_seg,data=cust_360)

summary(fit_age)

cust_360%>%group_by(age_seg)%>%
  summarise(tot_cust = n(),
            avg = mean(churn))



### 2. Gender has no impact


cust_360 %>% group_by(gender) %>% summarise(tot_cust = n(),
            avg = mean(churn))

### 3. No impact

cust_360 %>% group_by(gender) %>% summarise(tot_cust = n(),avg_age = mean(age))

### 4. 

fit_cust_cat <- aov(churn ~ custcat , data = cust_360)
summary(fit_cust_cat)

cust_360 %>% group_by(custcat) %>% summarise(tot_cust = n(), avg = mean(churn))

### 5. Customer category vs gender bias
require(gmodels)
cust_360 %>% group_by(custcat,gender) %>% summarise(totalCustomer = n())


CrossTable(cust_360$custcat , cust_360$gender)

### 6. Reside and churn

cust_360 %>% group_by(address) %>% summarise(totalCustomer = n(),avg=mean(churn))


### 7. Maritial Status and Education Level

cust_360 %>% group_by(ed,marital) %>% summarise(totalCustomer=n()) 

### 8. Retire and Churn
##Churn Rate is Less in Retire Customer

cust_360 %>% group_by(retire) %>% summarise(totalCustomer=n(),avg=mean(churn))

### 9. Tollfree service have no effect on churn rate; Others do

cust_360 %>% group_by(tollfree) %>% summarise(totalCustomer=n(),avg=mean(churn))
cust_360 %>% group_by(equip) %>% summarise(totalCustomer=n(),avg=mean(churn))
cust_360 %>% group_by(callcard) %>% summarise(totalCustomer=n(),avg=mean(churn))
cust_360 %>% group_by(wireless) %>% summarise(totalCustomer=n(),avg=mean(churn))


### 10. No impact

cust_360 %>% group_by(region) %>% summarise(totalCustomer=n(),avg=mean(churn))
```

