---
title: "HypothesisTesting"
author: "Harmandeep Singh"
date: "27 November 2017"
output: html_document
---
```{r,echo=FALSE}
cust_seg <- read.csv("E:/R-Programing/HypothesisTesting/cust_seg.csv")

```
# Case Study - 3
#### The dataset(cust_seg) is informstion of 200 customers who were part of the last campaign conducted by one of the major bank credit card division.

#### **Problem-1 :** Card Usage has been improved significantly from the last year usage which is 50

**Solution :**  One sample T-Test  
            Ho : Sample Average = 50  
            Ha : Sample Average <> 50  
```{r}
t.test(cust_seg$Post_usage_1month,mu=50)
```
#### *Conclusion :*  
P-Value < 0.05  
At 95% Confidence Level we can Reject Null Hypothesis.  
*Therefore, we can say that the average spends has been inceased from last year.*  
  

#### **Problem-2 : ** Last campaign was successful in terms of Credit card usage.

**Solution : ** Two Sample T-Test  

Ho : Pre-Average = Post-Average  
Ha : Pre-Average <> Post-Average  

```{r}
t.test(cust_seg$Post_usage_1month,cust_seg$pre_usage,paired = TRUE)
```

#### *Conclusion :*  
P-Value > 0.05  
At 95% Confidence Level we cannot Reject Null Hypothesis.  
*Therefore, Pre usage of credit card if not much affected by the campaign. As a result last campaign was not successful.  *


#### **Problem-3 : ** Is there any diffrence between males and females in terms of Credit card Usage.

**Solution** : Independent Group Test - Compare means for the two different samples  
Ho : Average spend of males = Average spend of females  
Ha : Average spend of males <> Average spend of females                

```{r}
t.test(Latest_mon_usage ~ sex, data = cust_seg, var.equal = TRUE)
```

P-Value > 0.05  
At 95% confidence level we cannot reject the null Hypothesis.  
*Therefore, Difference between credit card usage of Males and females is not different*  


#### **Problem-4 : ** Is there any difference between segments of customers in terms of credit card usage
<!--Annova : F Statistics-->

**Solution** : Multiple sample test : Comapring means of different segment of customer.  
Ho : Segment-1 = Segment-2 = Segment-3  
Ha : Segment-1 <> Segment-2 <> Segment-3  

```{r}
Anova_Segment = aov(Latest_mon_usage ~ segment,data=cust_seg)
summary(Anova_Segment)
```

*Conclusion : *
*F-Value is high, P-Value is low < 0.05  *  
*P-Value is low, We can reject null hypothesis  *  

**Therefore, there is difference between segments of customers in terms of credit card usage**

```{r,echo=FALSE}
model.tables(Anova_Segment,"means")

```

#### **Problem-5 :** Is there any relationship between Region and Segment  

**Solution : ** ChiSquare test : Comparing two catogorical variables.  
Ho : There is no relationship  
Ha : There is relationship  

```{r}
chisq.test(cust_seg$region,cust_seg$segment)
```

P-value < 0.05  
Therefore, We can say that there is some relationship between the region and segment

```{r,echo=FALSE}
tab <- xtabs(~region + segment, data = cust_seg)
tab
```


#### **Problem-6 : ** Is there any relationship between latest month and pre usage

```{r}
cor.test(cust_seg$Latest_mon_usage,cust_seg$pre_usage, use="pairwise.complete.obs")
```

Latest month Usage and Pre Usage is correlated with each other.